A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-03-02 sections/Appendix.tex
newpage before appendix; move measures to appendix; new ==>> symbol
Better-looking worklist measure figure taking more spaces
typo

@@

All but two cases can be finished easily following the declarative typing derivation,
and the proof shares a similar structure to DK's.
One tricky case related to Rule $\mathtt{Decl\forall I}$ inducates that $A$ has the shape $\all A_0$,
thus the subtyping relation derives from either $\mathtt{{\le}\forall L}$ or $\mathtt{{\le}\forall R}$.
For each of the case, the third measure $|A|_\forall + |A'|_\forall$ decreases
(the $\mathtt{{\le}\forall L}$ case requires a type substitution lemma obtaining
$\Psi \vdash e \Lto [\tau/a]A_0$ from the typing derivation).

>>>>

\subsection{Formal Definitions for Worklist Measures}

\begin{figure}[h!]
\hfill \framebox{$|\Gm|_e$} \hfill  \llap{Size measure.}
\begin{gather*}
    \begin{aligned}
    |\Gm|_e &= \sum_{e\Lto A\in\Gm}|e|_e + \sum_{e\To_a \jg\in\Gm}|e|_e +
        \sum_{\appInfAlg{A}{e}\in\Gm}|e|_e\\
    \text{where } |x|_e &= |()|_e = 1\\
        \qquad |\lam e|_e &= |e|_e + 1\\
        |e_1~e_2|_e &= |e_1|_e + |e_2|_e + 1\\
        |e:A|_e &= |e| + 1
    \end{aligned}
    \end{gather*}
    \hfill \framebox{$|\Gm|_\Leftrightarrow$} \hfill  \llap{Judgment measure.}
    \begin{gather*}
    \begin{aligned}
    |\Gm|_\Leftrightarrow &= 2\cdot\#_{e\Lto A\in\Gm} +
        \#_{e\To_a \jg\in\Gm} + 3\cdot\#_{\appInfAlg{A}{e}\in\Gm}
    \end{aligned}
    \end{gather*}
    \hfill \framebox{$|\Gm|_\forall$} \hfill  \llap{Polymorphism measure.}
    \begin{gather*}
    \begin{aligned}
    |\Gm|_\forall &= \sum_{e\Lto A\in\Gm}|A|_\forall + \sum_{\appInfAlg{A}{e}\in\Gm}|A|_\forall +
        \sum_{A\le B\in\Gm} |A|_\forall + |B|_\forall\\
    \text{where } |1|_\forall &= |a|_\forall = |\al|_\forall = 1\\
        |A\to B|_\forall &= |A|_\forall + |B|_\forall\\
        |\all A|_\forall &= |A|_\forall + 1
    \end{aligned}
    \end{gather*}
    \hfill \framebox{$|\Gm|_\to$} \hfill  \llap{Function measure.}
    \begin{gather*}
    \begin{aligned}
    |\Gm|_\to &= \sum_{e\Lto A\in\Gm}|A|_\to + \sum_{\appInfAlg{A}{e}\in\Gm}|A|_\to +
        \sum_{A\le B\in\Gm} |A|_\to + |B|_\to\\
    \text{where } |1|_\to &= |a|_\to = |\al|_\to = 1\\
        |A\to B|_\to &= |A|_\to + |B|_\to + 1\\
        |\all A|_\to &= |A|_\to
    \end{aligned}
    \end{gather*}
    \hfill \framebox{$|\Gm|_{\al}$} \hfill  \llap{Existential measure.}
    \begin{gather*}
    \begin{aligned}
    |\Gm|_{\al} &= \#_{\al\in\Gm}\\
    \end{aligned}
\end{gather*}
\caption{Worklist measures}
\label{fig:measures}
\end{figure}

@@

All but two cases can be finished easily following the declarative typing derivation,
and the proof shares a similar structure to DK's.
One tricky case related to Rule $\mathtt{Decl\forall I}$ indicates that $A$ has the shape $\all A_0$,
thus the subtyping relation derives from either $\mathtt{{\le}\forall L}$ or $\mathtt{{\le}\forall R}$.
For each of the case, the third measure $|A|_\forall + |A'|_\forall$ decreases
(the $\mathtt{{\le}\forall L}$ case requires a type substitution lemma obtaining
$\Psi \vdash e \Lto [\tau/a]A_0$ from the typing derivation).
